\bibliographystyle{IEEEtran}
\begin{thebibliography}{1}

\bibitem{zhang2020startup}
Y. Zhang, L. Chen, and M. Wang, "Survival analysis for startup success prediction," \textit{Journal of Business Research}, vol. 115, pp. 1--12, 2020.

\bibitem{kim2019ml}
S. Kim, J. Lee, and H. Park, "Machine learning approaches for startup performance prediction," \textit{Expert Systems with Applications}, vol. 125, pp. 1--15, 2019.

\bibitem{wang2021sentiment}
L. Wang, R. Brown, and K. Johnson, "Sentiment analysis for startup ecosystem prediction," \textit{Information Processing \& Management}, vol. 58, no. 3, pp. 1--18, 2021.

\bibitem{liu2022financial}
M. Liu, S. Zhang, and W. Chen, "Financial ratio-based startup prediction models," \textit{Journal of Business Venturing}, vol. 37, no. 2, pp. 1--22, 2022.

\bibitem{devlin2019bert}
J. Devlin, M. Chang, K. Lee, and K. Toutanova, "BERT: Pre-training of deep bidirectional transformers for language understanding," \textit{NAACL}, pp. 4171--4186, 2019.

\bibitem{hutto2014vader}
C. Hutto and E. Gilbert, "VADER: A parsimonious rule-based model for sentiment analysis of social media text," \textit{ICWSM}, pp. 216--225, 2014.

\bibitem{zhang2021news}
K. Zhang, Y. Li, and M. Wang, "News-driven financial prediction using deep learning," \textit{Expert Systems with Applications}, vol. 168, pp. 1--12, 2021.

\bibitem{chen2020event}
J. Chen, L. Wang, and R. Brown, "Event-driven prediction models for financial markets," \textit{Journal of Financial Data Science}, vol. 2, no. 3, pp. 45--62, 2020.

\bibitem{glasserman2013monte}
P. Glasserman, \textit{Monte Carlo Methods in Financial Engineering}. Springer, 2013.

\bibitem{cont2010network}
R. Cont, A. Moussa, and E. Santos, "Network structure and systemic risk in banking systems," \textit{Handbook on Systemic Risk}, pp. 327--368, 2010.

\bibitem{acharya2017systemic}
V. Acharya, T. Philippon, M. Richardson, and N. Roubini, "Measuring systemic risk," \textit{Review of Financial Studies}, vol. 30, no. 1, pp. 2--47, 2017.

\bibitem{allen2010understanding}
F. Allen, A. Babus, and E. Carletti, "Understanding financial crises," \textit{Annual Review of Financial Economics}, vol. 2, pp. 77--100, 2010.

\bibitem{lawrence2019argument}
J. Lawrence, C. Reed, C. Allen, S. McAlister, A. Ravenscroft, and L. Bourget, "Mining arguments from 19th century philosophical texts using topic based modelling," \textit{ACL}, pp. 6076--6086, 2019.

\bibitem{stede2018argument}
M. Stede and A. Schneider, "Argumentation mining," \textit{Synthesis Lectures on Human Language Technologies}, vol. 11, no. 2, pp. 1--145, 2018.

\bibitem{habernal2018argument}
I. Habernal, M. Wachsmuth, I. Gurevych, and B. Stein, "Argumentation mining in user-generated web discourse," \textit{Computational Linguistics}, vol. 44, no. 1, pp. 1--69, 2018.

\bibitem{li2020policy}
W. Li, J. Chen, and M. Wang, "Policy impact assessment using natural language processing," \textit{Policy Studies}, vol. 41, no. 4, pp. 456--478, 2020.

\bibitem{velivckovic2017graph}
P. Veličković, G. Cucurull, A. Casanova, A. Romero, P. Liò, and Y. Bengio, "Graph attention networks," \textit{ICLR}, 2018.

\bibitem{pearl2009causality}
J. Pearl, \textit{Causality: Models, Reasoning, and Inference}. Cambridge University Press, 2009.

\bibitem{kalisch2012causal}
M. Kalisch and P. Bühlmann, "Causal structure learning and inference: A selective review," \textit{Quality Technology \& Quantitative Management}, vol. 11, no. 1, pp. 3--21, 2012.

\bibitem{sharma2019causal}
K. Sharma, A. Zhang, and M. Liu, "Causal inference in financial time series," \textit{Journal of Financial Econometrics}, vol. 17, no. 2, pp. 234--256, 2019.

\end{thebibliography}

\end{document}
